Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-14 main.tex
Completed a lot more changes - many wording consistencies - many equation numbering consistencies - many notation consistencies - some figures updated a little bit as well - etc... - 2 additions remain

% Title, preferably not more than 10 words.
\title{Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}}

@@

The remainder of the paper is structured as follows. In Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties. Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it. Sections \ref{sec:loc_prelim} and \ref{sec:private_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the secure aggregation scheme. We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.

@@

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a | b$ stands for ``$a$ divides $b$'', and $a\|b$ for a bitwise concatenation of $a$ and $b$. Sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

    \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}. Although theoretically ideal for many privacy-preserving tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.

@@

    \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}. It is suitable for privacy-preserving distributed data as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier. While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.

@@

To support multiple aggregations at each time step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (3.375,3.375) rectangle (5.625,2.625);
    \node at (4.5,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
    \fill [lightgray] (0.875,3.375) rectangle (3.125,2.625);
    \node at (2,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

@@

In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.

@@

    A problem caused by this requirement is apparent in the context of aircraft navigation. It may be the case that some sensors are not within the range of a navigator broadcast. We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party. An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localisation instances with global broadcasts.
    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors. This means the navigator may not send different information to individual sensors during a single timestep.

@@

Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
\begin{equation*}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation*}
and sent to the aggregator.

@@

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, private summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}m^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{m_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{m_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}m_{i,t}} \pmod{N^2}
    \end{split}
\end{equation*}
removing all noise terms.

@@

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarised by the two informal security notions:
\begin{description}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances. Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=1}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
\end{description}

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a value $a$ and computes an encryption of $a$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(a)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

    % Adversaries and challenger
    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
    \draw [-latex] (2,1.75) -- (2,2.75);

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
    \draw [-latex] (2,4.5) --(2,5);

@@

\section{Private Localisation Preliminaries} \label{sec:loc_prelim}
Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localisation filter. The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model. We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.

@@

\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$. For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing. We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.

We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$. This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two. Rational subset $\mathbb{Q}_{r,f}$ is given by
\begin{equation*}
    \mathbb{Q}_{r,f} = \left\{q : f^{-1} | q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
\end{equation*}
and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$. That is, $\argmin_{q\in\mathbb{Q}_{r,f}} |x-q|$. In this form, mapping rationals $\mathbb{Q}_{r,f}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $r=N$, and handling negatives with modulo arithmetic. In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme. This is captured by a third parameter $m$; the number of multiplication factors to add or remove from encodings.

@@

The choice of a high fractional precision $f$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications. Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
\begin{equation*}
    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{r}{2} \right\rfloor\,.
\end{equation*}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $r=N$.

@@

\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
Given our definitions for the aggregation scheme in Section \ref{subsec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}. We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}. Received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.

>>>>

% Title, preferably not more than 10 words.
\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}}

@@

The remainder of the paper is structured as follows. In Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties. Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it. Sections \ref{sec:loc_prelim} and \ref{sec:priv_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the private aggregation scheme. We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.

@@

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

    \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}. Although theoretically ideal for many data-sensitive tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.

@@

    \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}. It is suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier. While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.

@@

To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (3.375,3.375) rectangle (5.625,2.625);
    \node at (4.5,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
    \fill [lightgray] (0.875,3.375) rectangle (3.125,2.625);
    \node at (2,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

@@

In Section \ref{sec:priv_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.

@@

    A problem caused by this requirement is apparent in the context of aircraft navigation. It may be the case that some sensors are not within the range of a navigator broadcast. We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party. An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localisation instances with global broadcasts.
    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors. This means the navigator may not send different information to individual sensors during a single time-step.

@@

Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}m^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{m_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{m_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}m_{i,t}} \pmod{N^2}
    \end{split}
\end{equation*}
removing all noise terms.

@@

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarised by the two informal security notions:
\begin{description}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances. Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$.
\end{description}

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a value $a$ and computes an encryption of $a$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(a)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

    % Adversaries and challenger
    \node at (3.25,3.25) {\Large$\mathcal{A}'$};
    \node at (3.25,5.5) {\Large$\mathcal{A}$};
    \node at (3.25,0.5) {\Large$\mathcal{C}$};

    % Arrows
    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO secure\\scheme};
    \draw [-latex] (2,1.75) -- (2,2.75);

    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO secure\\scheme};
    \draw [-latex] (2,4.5) --(2,5);

@@

\section{Encrypted Localisation Preliminaries} \label{sec:loc_prelim}
Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localisation filter. The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model. We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.

@@

\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x \,|\, x \in \mathbb{Z}_N\}$. For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing. We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.

We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$. This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two. Rational subset $\mathbb{Q}_{r,f}$ is given by
\begin{equation}
    \mathbb{Q}_{r,f} = \left\{q \,|\, f^{-1}\ \textsf{divides}\ q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
\end{equation}
and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$. That is, $\argmin_{q\in\mathbb{Q}_{r,f}} |x-q|$. In this form, mapping rationals $\mathbb{Q}_{r,f}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $r=N$, and handling negatives with modulo arithmetic. In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme. This is captured by a third parameter $m$; the number of multiplication factors to add or remove from encodings.

@@

The choice of a high fractional precision $f$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications. Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
\begin{equation}
    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{r}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $r=N$.

@@

\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
With the relevant preliminaries, we now apply the LCAO secure scheme to our original localisation problem. Recall we are considering a navigator in the presence of $n$ range sensors. The navigator runs a local filter, computing its update step with equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}, where received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time-step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
